### 2010-11-08 docs/tex/model.tex
Dynamics of mimicry
Mimicry chapter mostly complete

\begin{quotation}
``Modeling, it should be clear is an art form. It depends on the experience and taste of the modeler. In this it is much like cartooning. The modeler (cartoonist) must decide which features to make salient (exaggerate), and which features to eliminate (avoid), in order to answer the questions (make the political point)" \cite{holland1996}.
\end{quotation}

@@

>>>>

\begin{quotation}
``Modeling, it should be clear is an art form. It depends on the experience and taste of the modeler. In this it is much like cartooning. The modeler (cartoonist) must decide which features to make salient (exaggerate), and which features to eliminate (avoid), in order to answer the questions (make the political point)" - John H. Holland \cite{holland1996}.
\end{quotation}

@@

%Content needs to be added.....
\subsection{Reflection of punctuated equilibrium}
